---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# timethis

`timethis` is a simple package for modifying functions and expressions to return both the results and the execution time in a single list.

## Installation

You can install the released version of timethis from [CRAN](https://CRAN.R-project.org) with:

```{r install-rel, eval = FALSE}
install.packages("timethis")
```

Install the development version from GitHub with:

```{r install-dev, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mstrimas/timethis")
```

## Usage

To time an expression or chunk of R code use `time_this()`. This will return a list with elements `result` and `time` containing the results of evaluating the code and the executuion time (calculated with `system.time()`), respectively.

```{r time-this}
library(timethis)

# time a simple expression
time_this(mean(rnorm(1e6)))

# time a code chunk
time_this({
  x <- (1:1e6) / 1e6
  y = 2 * x + 1 + rnorm(x)
  lm(y ~ x)
})
```

Use `add_timer()` to wrap an existing function so its execution is timed with `system.time()` and both the results of the funciton call and the execution time are returned as a list.

```{r add-timer}
mean_timed <- add_timer(mean)
mean_timed(rnorm(1e6))

lm_timed <- add_timer(lm)
x <- (1:1e6) / 1e6
y = 2 * x + 1 + rnorm(x)
lm_timed(y ~ x)
```

